\documentclass[10pt, letterpaper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

% Custom Colors
\definecolor{primary}{RGB}{0, 51, 102}

% Formatting
\pagestyle{empty}
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{6pt}
\setlist[itemize]{noitemsep, topsep=1pt, leftmargin=1.5em}

\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    filecolor=primary,      
    urlcolor=primary,
}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{Akshat Grover}} \\
    \vspace{6pt}
    Bhopal, India $|$ \href{https://github.com/singh199908}{github.com/singh199908} \\
    \href{mailto:your.email@example.com}{your.email@example.com} $|$ +91-XXXXXXXXXX
\end{center}

% Education
\section{Education}
\textbf{Vellore Institute of Technology (VIT)}, Bhopal \hfill 2023 -- 2027 \\
\textit{Bachelor of Technology (B.Tech)} \hfill Current GPA: X.X/10.0

% Skills
\section{Technical Skills}
\begin{itemize}
    \item \textbf{Languages:} Python (Advanced), C++, JavaScript, Shell Scripting, HTML5/CSS3
    \item \textbf{CAD/BIM:} PythonOCC, IfcOpenShell, OpenCASCADE, IFC4/BIM Standards
    \item \textbf{AI \& Computer Vision:} OpenCV, CHAOS-ai Framework, Image Processing
    \item \textbf{Developer Tools:} Git/GitHub, Linux/Termux, LaTeX, Docker, Ngrok
    \item \textbf{Relevant Interests:} Structural Software Development, Open Source, Cybersecurity, Automation
\end{itemize}

% Projects
\section{Key Projects}

\textbf{Osdag IFC Wrapper (FOSSEE Contribution)} \hfill \textit{Feb 2026}
\begin{itemize}
    \item Engineered a custom **IFC Exporter** for Osdag (Steel Design Software) using **PythonOCC**.
    \item Implemented a robust geometry pipeline to translate 3D B-Rep (Boundary Representation) models into BIM-compatible **IFC4** files.
    \item Developed an automated triangulation engine using \textit{BRepMesh} to ensure cross-platform visibility in BIM viewers (BIMvision, Revit).
    \item Simplified complex topological data into semantic BIM entities, enabling structural interoperability.
\end{itemize}

\textbf{VIT Crowd Detection \& Amber Alert (CROWD\_AMBER\_v3)} \hfill \textit{Python, OpenCV}
\begin{itemize}
    \item Built an end-to-end intelligent safety system for campus environments using **Computer Vision**.
    \item Leveraged OpenCV for real-time crowd density estimation and automated alert triggering.
    \item Integrated an Amber Alert notification system for rapid response to safety incidents.
    \item Open-sourced the project under the MIT license, emphasizing community safety technology.
\end{itemize}

\textbf{CHAOS-ai Framework} \hfill \textit{Python}
\begin{itemize}
    \item Developed a versatile AI toolkit focused on automation and intelligent scripting.
    \item Optimized for lightweight performance in local environments, showcasing modular software design.
\end{itemize}

\textbf{VITcoin (Blockchain & Fintech Innovation)} \hfill \textit{Shell, JavaScript}
\begin{itemize}
    \item Experimented with decentralized ledger concepts tailored for campus-wide digital transactions.
    \item Developed a proof-of-concept for digital currency management using efficient shell-based logic.
\end{itemize}

\textbf{sin-s-script (Advanced Automation & Security)} \hfill \textit{HTML, Python, Ngrok}
\begin{itemize}
    \item Created a high-level automation tool utilizing Web APIs, Ngrok, and Shell scripts for remote system monitoring.
    \item Demonstrated deep understanding of networking protocols, location services, and credential security.
\end{itemize}

% Experience / Open Source
\section{Experience \& Initiatives}
\begin{itemize}
    \item \textbf{FOSSEE Screening:} Successfully developed complex wrappers for structural engineering software, proving capability in industrial-grade Python development.
    \item \textbf{Open Source Contributor:} Maintained 20+ public repositories on GitHub with over 4 years of continuous development history.
    \item \textbf{Cybersecurity Research:} Explored various attack-vector simulations and defense mechanisms through projects like TBomb and WellsBalChecker.
\end{itemize}

\end{document}
